An Axiomatic Basis for Computer Programming: Review

### 2017-02-14 hoare/paper.tex
Add postcondition for quadratic equation

  This is review on C.A.R. Hoare's paper, An Axiomatic Basis for Computer
  Programming.

@@

We limits input domain as set of real numbers and according to discriminant in
predicate P:
$$ P \equiv (a, b, c \in \mathbb{R}) \wedge (b^2 - 4ac \geq 0)$$

Then we could find values by some program Q. And finally check
whether equation holds or not in R.

>>>>

  This is review on C.A.R. Hoare's paper, An Axiomatic Basis for Computer
  Programming.
  (WIP)

@@

We limits input domain as set of real numbers and according to discriminant in
predicate P (suppose we used general quadratic formula):
$$ P \equiv (a, b, c \in \mathbb{R}) \wedge (b^2 - 4ac \geq 0)$$

Then we could find values by some program Q.
And finally check whether equation holds or not in R: 
$$ R \equiv (X \subseteq \mathbb{R}) \wedge (\forall x \in X \bullet ax^2 + bx + c
= 0)$$
